---
title: "Describe exchange rate and volume"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```
```{r}
library(BlockChain)
library(foreach)
library(magrittr)
library(doParallel)
library(ggpubr)
library(kableExtra)
```


```{r}
# --------- #
# load data
# --------- #
rate <- readRDS(file = here::here("cleaned/currency_rate_date_yahoo.rds"))
rate_estimate <- readRDS(file = here::here("output/rate_estimate.rds"))
```

```{r}
colour_palette <- 
  c(
    "BTC" = "#F7931A",
    "BCH" = "#0AC18E",
    "BSV" = "#00368C"
  )
```


# Level {.tabset}

```{r}
exogenous_process <-
  rate %>%
  dplyr::filter(
    currency == "BTC" |
      currency == "BCH" |
      currency == "BSV"
  ) %>%
  dplyr::arrange(currency, date) %>%
  dplyr::group_by(currency) %>%
  dplyr::mutate(
    dplyr::across(
      .cols = c(rate_quoteusd, volume),
      .fns = ~ . - dplyr::lag(.)
    )
  ) %>%
  dplyr::filter(is.finite(rate_quoteusd), is.finite(volume)) %>%
  dplyr::mutate(
    dplyr::across(
      .cols = c(rate_quoteusd, volume),
      .fns = ~ (. - mean(.)) / sd(.)
    )
  ) %>%
  dplyr::ungroup()
   
```


## Normal distribution {.tabset}


### Exchange rate {.tabset}


```{r}
p <-
  exogenous_process %>%
  dplyr::group_split(currency) %>%
  purrr::map(
    .,
    ~ ggplot(
      data = .,
      aes(
        sample = rate_quoteusd
        )
      ) +
      geom_qq() +
      geom_qq_line() +
      theme_classic()
  )
```

```{r, results = "asis"}
# draw time series 
currency_list <-
  unique(exogenous_process$currency)
for (i in 1:length(p)) {
  cat("\n\n")
  cat("####", currency_list[i], "\n\n")
  print(p[[i]])
  cat("\n\n")
}
```


### Transaction volume {.tabset}


```{r}
p <-
  exogenous_process %>%
  dplyr::group_split(currency) %>%
  purrr::map(
    .,
    ~ ggplot(
      data = .,
      aes(
        sample = volume
        )
      ) +
      geom_qq() +
      geom_qq_line() +
      theme_classic()
  )
```

```{r, results = "asis"}
# draw time series 
currency_list <-
  unique(exogenous_process$currency)
for (i in 1:length(p)) {
  cat("\n\n")
  cat("####", currency_list[i], "\n\n")
  print(p[[i]])
  cat("\n\n")
}
```


## t distribution {.tabset}


### Exchange rate {.tabset}


```{r, results = "asis"}
p <-
  exogenous_process %>%
  dplyr::group_split(currency) %>%
  purrr::map(
    .,
    ~ fitdistrplus::fitdist(
      data = .$rate_quoteusd,
      distr = "t",
      start = list(df = 2),
      method = "mle"
      ) %>%
      fitdistrplus::qqcomp(
        .,
        plotstyle = "ggplot",
        xlim = c(-5, 5)
      ) +
      theme_classic()
  )
# draw time series 
currency_list <-
  unique(exogenous_process$currency)
for (i in 1:length(p)) {
  cat("\n\n")
  cat("####", currency_list[i], "\n\n")
  print(p[[i]])
  cat("\n\n")
}
```


### Transaction volume {.tabset}


```{r, results = "asis"}
p <-
  exogenous_process %>%
  dplyr::group_split(currency) %>%
  purrr::map(
    .,
    ~ fitdistrplus::fitdist(
      data = .$volume,
      distr = "t",
      start = list(df = 2),
      method = "mle"
      ) %>%
      fitdistrplus::qqcomp(
        .,
        plotstyle = "ggplot",
        xlim = c(-5, 5)
      ) +
      theme_classic()
  )
# draw time series 
currency_list <-
  unique(exogenous_process$currency)
for (i in 1:length(p)) {
  cat("\n\n")
  cat("####", currency_list[i], "\n\n")
  print(p[[i]])
  cat("\n\n")
}
```


## Cauchy distribution {.tabset}


### Exchange rate {.tabset}


```{r, results = "asis"}
p <-
  exogenous_process %>%
  dplyr::group_split(currency) %>%
  purrr::map(
    .,
    ~ fitdistrplus::fitdist(
      data = .$rate_quoteusd,
      distr = "cauchy",
      method = "mle"
      ) %>%
      fitdistrplus::qqcomp(
        .,
        plotstyle = "ggplot",
        xlim = c(-5, 5)
      ) +
      theme_classic()
  )
# draw time series 
currency_list <-
  unique(exogenous_process$currency)
for (i in 1:length(p)) {
  cat("\n\n")
  cat("####", currency_list[i], "\n\n")
  print(p[[i]])
  cat("\n\n")
}
```


### Transaction volume {.tabset}


```{r, results = "asis"}
p <-
  exogenous_process %>%
  dplyr::group_split(currency) %>%
  purrr::map(
    .,
    ~ fitdistrplus::fitdist(
      data = .$volume,
      distr = "cauchy",
      method = "mle"
      ) %>%
      fitdistrplus::qqcomp(
        .,
        plotstyle = "ggplot",
        xlim = c(-5, 5)
      ) +
      theme_classic()
  )
# draw time series 
currency_list <-
  unique(exogenous_process$currency)
for (i in 1:length(p)) {
  cat("\n\n")
  cat("####", currency_list[i], "\n\n")
  print(p[[i]])
  cat("\n\n")
}
```


# Log {.tabset}

```{r}
exogenous_process <-
  rate %>%
  dplyr::filter(
    currency == "BTC" |
      currency == "BCH" |
      currency == "BSV"
  ) %>%
  dplyr::arrange(currency, date) %>%
  dplyr::group_by(currency) %>%
  dplyr::mutate(
    dplyr::across(
      .cols = c(rate_quoteusd, volume),
      .fns = ~ log(.)
    )
  ) %>%
  dplyr::mutate(
    dplyr::across(
      .cols = c(rate_quoteusd, volume),
      .fns = ~ . - dplyr::lag(.)
    )
  ) %>%
  dplyr::filter(is.finite(rate_quoteusd), is.finite(volume)) %>%
  dplyr::mutate(
    dplyr::across(
      .cols = c(rate_quoteusd, volume),
      .fns = ~ (. - mean(.)) / sd(.)
    )
  ) %>%
  dplyr::ungroup()
   
```


## Normal distribution {.tabset}


### Exchange rate {.tabset}


```{r}
p <-
  exogenous_process %>%
  dplyr::group_split(currency) %>%
  purrr::map(
    .,
    ~ ggplot(
      data = .,
      aes(
        sample = rate_quoteusd
        )
      ) +
      geom_qq() +
      geom_qq_line() +
      theme_classic()
  )
```

```{r, results = "asis"}
# draw time series 
currency_list <-
  unique(exogenous_process$currency)
for (i in 1:length(p)) {
  cat("\n\n")
  cat("####", currency_list[i], "\n\n")
  print(p[[i]])
  cat("\n\n")
}
```


### Transaction volume {.tabset}


```{r}
p <-
  exogenous_process %>%
  dplyr::group_split(currency) %>%
  purrr::map(
    .,
    ~ ggplot(
      data = .,
      aes(
        sample = volume
        )
      ) +
      geom_qq() +
      geom_qq_line() +
      theme_classic()
  )
```

```{r, results = "asis"}
# draw time series 
currency_list <-
  unique(exogenous_process$currency)
for (i in 1:length(p)) {
  cat("\n\n")
  cat("####", currency_list[i], "\n\n")
  print(p[[i]])
  cat("\n\n")
}
```


## t distribution {.tabset}


### Exchange rate {.tabset}


```{r, results = "asis"}
p <-
  exogenous_process %>%
  dplyr::group_split(currency) %>%
  purrr::map(
    .,
    ~ fitdistrplus::fitdist(
      data = .$rate_quoteusd,
      distr = "t",
      start = list(df = 10),
      method = "mle"
      ) %>%
      fitdistrplus::qqcomp(
        .,
        plotstyle = "ggplot",
        xlim = c(-5, 5)
      ) +
      theme_classic()
  )
# draw time series 
currency_list <-
  unique(exogenous_process$currency)
for (i in 1:length(p)) {
  cat("\n\n")
  cat("####", currency_list[i], "\n\n")
  print(p[[i]])
  cat("\n\n")
}
```


### Transaction volume {.tabset}


```{r, results = "asis"}
p <-
  exogenous_process %>%
  dplyr::group_split(currency) %>%
  purrr::map(
    .,
    ~ fitdistrplus::fitdist(
      data = .$volume,
      distr = "t",
      start = list(df = 10),
      method = "mle"
      ) %>%
      fitdistrplus::qqcomp(
        .,
        plotstyle = "ggplot",
        xlim = c(-5, 5)
      ) +
      theme_classic()
  )
# draw time series 
currency_list <-
  unique(exogenous_process$currency)
for (i in 1:length(p)) {
  cat("\n\n")
  cat("####", currency_list[i], "\n\n")
  print(p[[i]])
  cat("\n\n")
}
```


## Cauchy distribution {.tabset}


### Exchange rate {.tabset}


```{r, results = "asis"}
p <-
  exogenous_process %>%
  dplyr::group_split(currency) %>%
  purrr::map(
    .,
    ~ fitdistrplus::fitdist(
      data = .$rate_quoteusd,
      distr = "cauchy",
      method = "mle"
      ) %>%
      fitdistrplus::qqcomp(
        .,
        plotstyle = "ggplot",
        xlim = c(-5, 5)
      ) +
      theme_classic()
  )
# draw time series 
currency_list <-
  unique(exogenous_process$currency)
for (i in 1:length(p)) {
  cat("\n\n")
  cat("####", currency_list[i], "\n\n")
  print(p[[i]])
  cat("\n\n")
}
```


### Transaction volume {.tabset}


```{r, results = "asis"}
p <-
  exogenous_process %>%
  dplyr::group_split(currency) %>%
  purrr::map(
    .,
    ~ fitdistrplus::fitdist(
      data = .$volume,
      distr = "cauchy",
      method = "mle"
      ) %>%
      fitdistrplus::qqcomp(
        .,
        plotstyle = "ggplot",
        xlim = c(-5, 5)
      ) +
      theme_classic()
  )
# draw time series 
currency_list <-
  unique(exogenous_process$currency)
for (i in 1:length(p)) {
  cat("\n\n")
  cat("####", currency_list[i], "\n\n")
  print(p[[i]])
  cat("\n\n")
}
```

# Estimation results

## Estimated exchang rate

```{r}
rate_estimate_sha256 <-
  dplyr::bind_rows(
    rate_estimate %>%
    dplyr::filter(currency == "BTC"),
  rate_estimate %>%
    dplyr::filter(currency == "BCH"),
  rate_estimate %>%
    dplyr::filter(currency == "BSV")
  ) %>%
  dplyr::select(
    currency,
    rate_quoteusd_mean,
    rate_quoteusd_sd,
    rate_quoteusd_df
  )
rate_estimate_sha256 %>%
  magrittr::set_colnames(c("Curency", "Mean", "Sd", "Df")) %>%
  dplyr::mutate_if(
    is.numeric,
    ~ formatC(., digit = 4, format = "f")
  ) %>%
  kbl(
    booktabs = TRUE,
    align = c("l", rep("r", 3))
  ) %>%
  kable_styling()
```

# Export

```{r}
rate_estimate_sha256 %>%
  magrittr::set_colnames(c("Curency", "Mean", "Sd", "Df")) %>%
  dplyr::mutate_if(
    is.numeric,
    ~ formatC(., digit = 4, format = "f")
  ) %>%
  kbl(
    booktabs = TRUE,
    align = c("l", rep("r", 3)),
    format = "latex",
    linesep = ""
  ) %>%
  save_kable(
    file = here::here("figuretable/describe_exchange/rate_estimate.tex")
  )
```

