---
title: "Codebook of cleaned data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# -------------- #
# import library
# -------------- #
library(BlockChainPublic)
library(foreach)
library(magrittr)
library(kableExtra)
```

```{r}
# --------- #
# read data
# --------- #
# daily hashrate data
currency_blockheight_hashrate <- readRDS(file = here::here("cleaned/currency_blockheight_hashrate.rds"))
# daily hashrate data
currency_date_hashrate <- readRDS(file = here::here("cleaned/currency_date_hashrate.rds"))
# weekly hashrate data
currency_week_hashrate <- readRDS(file = here::here("cleaned/currency_week_hashrate.rds"))
# base reward data
reward <- readRDS(file = here::here("cleaned/currency_reawrd_date.rds"))
# currency rate data from kaiko
rate <- readRDS(file = here::here("cleaned/currency_rate_date.rds"))
# currency rate data from yahoo
rate_yahoo <- readRDS(file = here::here("cleaned/currency_rate_date_yahoo.rds"))
# asic machine
asic_list <- readRDS(file = here::here("cleaned/asic_list.rds"))
# gpu list
gpu_list <- readRDS(file = here::here("cleaned/gpu_list.rds"))
# asic trend
asic_trend <- readRDS(file = here::here("cleaned/asic_trend.rds"))
# gpu trend
gpu_trend <- readRDS(file = here::here("cleaned/gpu_trend.rds"))
```

# variables {.tabset}

## currency_blockheight_hashrate.rds

### key variables:

| column names | definition | unique values |
|--------------|------------|---------------|
| `currency`| symbol of the cryptocurrency | `r length(unique(currency_blockheight_hashrate$currency))` |
| `algo` | PoW algorithm used | `r length(unique(currency_blockheight_hashrate$algo))` |
| `blockheight` | height of the block | `r length(unique(currency_blockheight_hashrate$date))` |

### categorical Variables

| column names | definition | 
|--------------|------------|
| `bits` | bits of the block|


### numerical Variables

| column names | definition | unit |
|--------------|------------|------|
| `datetime` | the datetime of the block generation | YYYY-MM-DD HH-mm-ss |
| `winning_rate` | probability of win | probability per h/s hash |
| `block_time` | the average of the block generation time since the last generation | s | 
| `inverse_hash_rate` | inverse of the hash rate | 1/(h/s) | 
| `hash_rate` | average of the hash rate | h/s |
| `blockhash` | hash compared to the winning rate | real number between 0 and 1| 


```{r}
currency_blockheight_hashrate %>%
  modelsummary::datasummary_skim()
```


## currency_date_hashrate.rds

### key variables:

| column names | definition | unique values |
|--------------|------------|---------------|
| `currency`| symbol of the cryptocurrency | `r length(unique(currency_date_hashrate$currency))` |
| `algo` | PoW algorithm used | `r length(unique(currency_date_hashrate$algo))` |
| `date` | date of the record | `r length(unique(currency_date_hashrate$date))` |

### categorical Variables

- Nothing.

### numerical Variables

| column names | definition | unit |
|--------------|------------|------|
| `blockheight` | block height at the beginning of the date | block |
| `winning_rate` | probability of win | probability per h/s hash |
| `block_time` | the average of the block generation time since the last generation | s | 
| `inverse_hash_rate` | inverse of the hash rate | 1/(h/s) | 
| `hash_rate` | average of the hash rate | h/s |
| `hash_rate_sd` | standard deviation of the hash rate  | h/s |
| `block_time_sd` | standard deviation of the block time | s |


```{r}
currency_date_hashrate %>%
  modelsummary::datasummary_skim()
```

## currency_week_hashrate.rds

### key variables:

| column names | definition | unique values |
|--------------|------------|---------------|
| `currency`| symbol of the cryptocurrency | `r length(unique(currency_week_hashrate$currency))` |
| `algo` | PoW algorithm used | `r length(unique(currency_week_hashrate$algo))` |
| `week` | Sunday of the week of the record | `r length(unique(currency_week_hashrate$week))` |

### categorical Variables

- Nothing.

### numerical Variables

| column names | definition | unit |
|--------------|------------|------|
| `blockheight` | block height at the beginning of the week | block |
| `winning_rate` | probability of win | probability per h/s hash |
| `block_time` | the average of the block generation time since the last generation | s | 
| `inverse_hash_rate` | inverse of the hash rate | 1/(h/s) | 
| `hash_rate` | average of the hash rate | h/s |
| `hash_rate_sd` | standard deviation of the hash rate  | h/s |
| `block_time_sd` | standard deviation of the block time | s |


```{r}
currency_week_hashrate %>%
  modelsummary::datasummary_skim()
```


## currency_reward_date.rds

### key variables

| column names | definition | unique values |
|--------------|------------|---------------|
| `currency`| symbol of the cryptocurrency | `r length(unique(reward$currency))` |
| `date` | date of the record | `r length(unique(reward$date))` |

### categorical variables

- Nothing.

### numerical variables

| column names | definition | unit |
|--------------|------------|------|
| `reward` | reward of block generation | token/block | 

```{r}
reward %>% 
  modelsummary::datasummary_skim()  
```

## currency_rate_date.rds

### key variables

| column names | definition | unique values |
|--------------|------------|---------------|
| `currency`| symbol of the cryptocurrency | `r length(unique(rate$currency))` |
| `date` | date of the record | `r length(unique(rate$date))` |

### categorical variables

- Nothing.

### numerical variables

| column names | definition | unit |
|--------------|------------|------|
| `rate_quotebtc` | value of the currency in terms of btc | BTC/token |
| `rate_quoteusd` | value of the currency in terms of USD | USD/token |
| `volume` | transaction volume with USD for BTC and with BTC for others | Count |

```{r}
rate %>%
  modelsummary::datasummary_skim()
```

## currency_rate_date_yahoo.rds

### key variables

| column names | definition | unique values |
|--------------|------------|---------------|
| `currency`| symbol of the cryptocurrency | `r length(unique(rate_yahoo$currency))` |
| `date` | date of the record | `r length(unique(rate_yahoo$date))` |

### categorical variables

- Nothing.

### numerical variables

| column names | definition | unit |
|--------------|------------|------|
| `rate_quoteusd` | value of the currency in terms of USD | USD/token |
| `volume` | transaction volume with USD | Billion USD |

```{r}
rate_yahoo %>%
  modelsummary::datasummary_skim()
```

## asic_list.rds

### key variables

| column names | definition | unique values |
|--------------|------------|---------------|
| `model`| name of the asic machine | `r length(unique(asic_list$model))` |

### categorical variables

| column names | definition | 
|--------------|------------|
| `algo` | applicable PoW algorithm applicable|
| `release` | release date of the machine | 

```{r}
asic_list %>%
  dplyr::mutate(release = as.character(release)) %>%
  modelsummary::datasummary_skim(type = "categorical")
```


### numerical variables

| column names | definition | unit |
|--------------|------------|------|
| `hash_rate_spec` | hash power generate by the machine | h/s |
| `power` | power to obtain the hash rate | W |


```{r}
asic_list %>%
  modelsummary::datasummary_skim()
```

## gpu_list.rds

### key variables

| column names | definition | unique values |
|--------------|------------|---------------|
| `model`| name of the gpu machine | `r length(unique(gpu_list$model))` |

### categorical variables

| column names | definition | 
|--------------|------------|
| `algo` | applicable PoW algorithm applicable|
| `release` | release date of the machine | 

```{r}
gpu_list %>%
  dplyr::mutate(release = as.character(release)) %>%
  modelsummary::datasummary_skim(type = "categorical")
```


### numerical variables

| column names | definition | unit |
|--------------|------------|------|
| `hash_rate_spec` | hash power generate by the machine | h/s |
| `power` | power to obtain the hash rate | W |


```{r}
gpu_list %>%
  modelsummary::datasummary_skim()
```

## asic_trend.rds

### key variables

| column names | definition | unique values |
|--------------|------------|---------------|
| `model`| name of the asic machine | `r length(unique(asic_trend$model))` |
| `month` | initial date of the month | `r length(unique(asic_trend$month))`` |

### categorical variables

- Nothing.


### numerical variables

| column names | definition | unit |
|--------------|------------|------|
| `hits` | google trend hits | relative search volume within each keyword |


```{r}
asic_trend %>%
  modelsummary::datasummary_skim()
```

## gpu_trend.rds

### key variables

| column names | definition | unique values |
|--------------|------------|---------------|
| `model`| name of the asic machine | `r length(unique(gpu_trend$model))` |
| `month` | initial date of the month | `r length(unique(gpu_trend$month))`` |

### categorical variables

- Nothing.


### numerical variables

| column names | definition | unit |
|--------------|------------|------|
| `hits` | google trend hits | relative search volume within each keyword |


```{r}
gpu_trend %>%
  modelsummary::datasummary_skim()
```


# Export {.tabset}

```{r}
currency_blockheight_hashrate_sha256 <-
  currency_blockheight_hashrate %>%
  dplyr::filter(algo == "sha256")
currency_blockheight_hashrate_sha256 %>%
  dplyr::summarise(
    start = min(datetime),
    end = max(datetime)
  ) %>%
  kbl() %>%
  kable_styling()

table <-
  currency_blockheight_hashrate_sha256 %>%
  dplyr::group_by(currency) %>%
  dplyr::summarise(
    dplyr::across(
      .cols = c(winning_rate, block_time, hash_rate),
      .fns = list(
        n = length,
        mean = mean,
        sd = sd,
        min = min,
        max = max
      ),
      .names = "{.col}-{.fn}"
    )
  ) %>%
  tidyr::pivot_longer(
    cols = - 1,
    names_sep = "-",
    names_to = c("variable", "stat")
  ) %>%
  tidyr::pivot_wider(
    id_cols = c(currency, variable),
    names_from = stat,
    values_from = value
  ) 

table <-
  dplyr::bind_rows(
    table %>% dplyr::filter(currency == "BTC"),
    table %>% dplyr::filter(currency == "BCH"),
    table %>% dplyr::filter(currency == "BSV")
  )

table %>%
  dplyr::mutate_if(
    is.numeric,
    ~ formatC(., digit = 3)
  ) %>%
  dplyr::group_by(currency) %>%
  dplyr::mutate(
    currency = ifelse(dplyr::row_number() > 1, "", currency)
  ) %>%
  dplyr::mutate(
    variable = 
      dplyr::case_when(
        variable == "winning_rate" ~ "Winning rate",
        variable == "block_time" ~ "Block time (s)",
        variable == "hash_rate" ~ "Hash rate (h/s)"
      )
  ) %>%
  magrittr::set_colnames(
    Hmisc::capitalize(colnames(.))
  ) %>%
  kbl(
    booktabs = TRUE,
    align = c("l", "l", rep("r", ncol(.) - 2))
  ) %>%
  kable_styling()
table %>%
  dplyr::mutate_if(
    is.numeric,
    ~ formatC(., digit = 3)
  ) %>%
  dplyr::group_by(currency) %>%
  dplyr::mutate(
    currency = ifelse(dplyr::row_number() > 1, "", currency)
  ) %>%
  dplyr::mutate(
    variable = 
      dplyr::case_when(
        variable == "winning_rate" ~ "Winning rate",
        variable == "block_time" ~ "Block time (s)",
        variable == "hash_rate" ~ "Hash rate (H/s)"
      )
  ) %>%
  magrittr::set_colnames(
    Hmisc::capitalize(colnames(.))
  ) %>%
  kbl(
    booktabs = TRUE,
    align = c("l", "l", rep("r", ncol(.) - 2)),
    format = "latex",
    linesep = ""
  ) %>%
  save_kable(
    file = here::here("figuretable/summarize_cleaned_data/currency_height_sha256_summary.tex")
  )
```

```{r}
table <-
  currency_blockheight_hashrate_sha256 %>%
  dplyr::filter(datetime >= "2019-01-01") %>%
  dplyr::group_by(currency) %>%
  dplyr::summarise(
    dplyr::across(
      .cols = c(winning_rate, block_time, hash_rate),
      .fns = list(
        n = length,
        mean = mean,
        sd = sd,
        min = min,
        max = max
      ),
      .names = "{.col}-{.fn}"
    )
  ) %>%
  tidyr::pivot_longer(
    cols = - 1,
    names_sep = "-",
    names_to = c("variable", "stat")
  ) %>%
  tidyr::pivot_wider(
    id_cols = c(currency, variable),
    names_from = stat,
    values_from = value
  ) 

table <-
  dplyr::bind_rows(
    table %>% dplyr::filter(currency == "BTC"),
    table %>% dplyr::filter(currency == "BCH"),
    table %>% dplyr::filter(currency == "BSV")
  )

table %>%
  dplyr::mutate_if(
    is.numeric,
    ~ formatC(., digit = 3)
  ) %>%
  dplyr::group_by(currency) %>%
  dplyr::mutate(
    currency = ifelse(dplyr::row_number() > 1, "", currency)
  ) %>%
  dplyr::mutate(
    variable = 
      dplyr::case_when(
        variable == "winning_rate" ~ "Winning rate",
        variable == "block_time" ~ "Block time (s)",
        variable == "hash_rate" ~ "Hash rate (h/s)"
      )
  ) %>%
  magrittr::set_colnames(
    Hmisc::capitalize(colnames(.))
  ) %>%
  kbl(
    booktabs = TRUE,
    align = c("l", "l", rep("r", ncol(.) - 2))
  ) %>%
  kable_styling()
table %>%
  dplyr::mutate_if(
    is.numeric,
    ~ formatC(., digit = 3)
  ) %>%
  dplyr::group_by(currency) %>%
  dplyr::mutate(
    currency = ifelse(dplyr::row_number() > 1, "", currency)
  ) %>%
  dplyr::mutate(
    variable = 
      dplyr::case_when(
        variable == "winning_rate" ~ "Winning rate",
        variable == "block_time" ~ "Block time (s)",
        variable == "hash_rate" ~ "Hash rate (H/s)"
      )
  ) %>%
  magrittr::set_colnames(
    Hmisc::capitalize(colnames(.))
  ) %>%
  kbl(
    booktabs = TRUE,
    align = c("l", "l", rep("r", ncol(.) - 2)),
    format = "latex",
    linesep = ""
  ) %>%
  save_kable(
    file = here::here("figuretable/summarize_cleaned_data/currency_height_sha256_since2019_summary.tex")
  )
```



```{r}
rate_yahoo_sha256 <-
  rate_yahoo %>%
  dplyr::filter(
    currency == "BTC" |
      currency == "BCH" |
      currency == "BSV"
  )
rate_yahoo_sha256 %>%
  dplyr::group_by(currency) %>%
  dplyr::summarise(
    start = min(date),
    end = max(date)
  ) %>%
  kbl() %>%
  kable_styling()

table <-
  rate_yahoo_sha256 %>%
  dplyr::group_by(currency) %>%
  dplyr::summarise(
        n = sum(!is.na(rate_quoteusd), na.rm = TRUE),
        mean = mean(rate_quoteusd, na.rm = TRUE),
        sd = sd(rate_quoteusd, na.rm = TRUE),
        min = min(rate_quoteusd, na.rm = TRUE),
        max = max(rate_quoteusd, na.rm = TRUE)
  ) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    variable = "Price (USD)"
  ) %>%
  dplyr::select(currency, variable, dplyr::everything())

table <-
  dplyr::bind_rows(
    table %>% dplyr::filter(currency == "BTC"),
    table %>% dplyr::filter(currency == "BCH"),
    table %>% dplyr::filter(currency == "BSV")
  )

table %>%
  dplyr::mutate_if(
    is.numeric,
    ~ formatC(., digit = 1, format = "f")
  ) %>%
  magrittr::set_colnames(
    Hmisc::capitalize(colnames(.))
  ) %>%
  kbl(
    booktabs = TRUE,
    align = c("l", rep("r", ncol(.) - 1))
  ) %>%
  kable_styling()

table %>%
  dplyr::mutate_if(
    is.numeric,
    ~ formatC(., digit = 1, format = "f")
  ) %>%
  magrittr::set_colnames(
    Hmisc::capitalize(colnames(.))
  ) %>%
  kbl(
    booktabs = TRUE,
    align = c("l", rep("r", ncol(.) - 1)),
    format = "latex",
    linesep = ""
  ) %>%
  save_kable(
    file = here::here("figuretable/summarize_cleaned_data/currency_date_rate_sha256_summary.tex")
  )

```

```{r}
table <-
  rate_yahoo_sha256 %>%
  dplyr::filter(date >= "2019-01-01") %>%
  dplyr::group_by(currency) %>%
  dplyr::summarise(
        n = sum(!is.na(rate_quoteusd), na.rm = TRUE),
        mean = mean(rate_quoteusd, na.rm = TRUE),
        sd = sd(rate_quoteusd, na.rm = TRUE),
        min = min(rate_quoteusd, na.rm = TRUE),
        max = max(rate_quoteusd, na.rm = TRUE)
  ) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    variable = "Price (USD)"
  ) %>%
  dplyr::select(currency, variable, dplyr::everything())

table <-
  dplyr::bind_rows(
    table %>% dplyr::filter(currency == "BTC"),
    table %>% dplyr::filter(currency == "BCH"),
    table %>% dplyr::filter(currency == "BSV")
  )

table %>%
  dplyr::mutate_if(
    is.numeric,
    ~ formatC(., digit = 1, format = "f")
  ) %>%
  magrittr::set_colnames(
    Hmisc::capitalize(colnames(.))
  ) %>%
  kbl(
    booktabs = TRUE,
    align = c("l", rep("r", ncol(.) - 1))
  ) %>%
  kable_styling()

table %>%
  dplyr::mutate_if(
    is.numeric,
    ~ formatC(., digit = 1, format = "f")
  ) %>%
  magrittr::set_colnames(
    Hmisc::capitalize(colnames(.))
  ) %>%
  kbl(
    booktabs = TRUE,
    align = c("l", rep("r", ncol(.) - 1)),
    format = "latex",
    linesep = ""
  ) %>%
  save_kable(
    file = here::here("figuretable/summarize_cleaned_data/currency_date_rate_sha256_since2019_summary.tex")
  )
```


















